Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-01-05 paper.tex
created an outline, removed phd style

\documentclass{report}
\usepackage{cuthesis}
\usepackage{hyperref}
\usepackage{xcolor}
\author{Valerie Hayot-Sasson}
\title{Thesis Title}
\titleOfPhDAuthor{}          % or Ms., Mrs., Miss, etc. (only for PhD's)
\PhD                            % Masters by default
\degree{Computer Science}
% \dept{Computer Science}       % default is Comp.Sci.
\cosupervisor                   % if you also have a co-supervisor

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{document}
\begin{abstract}
  Text of abstract.  
\end{abstract}

\begin{acknowledgments}
  Text of acknowledgments.
\end{acknowledgments}

\chapter{Introduction}
intro here
\chapter{Parallelization frameworks}
\section{Databases}
\section{Pipelining engines}
\chapter{MapReduce}
Summary of ~\cite{mapred}

@@

\section{Apache Spark}
\cite{spark}
\chapter{MapReduce applications in neuroscience}
\cite{thunder}

\section{Schedulers}
\chapter{Pipelining engines used in neuroscience}
\cite{nipype}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Body of Thesis goes here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass{report}

\usepackage{hyperref}
\usepackage{xcolor}

@@

\begin{document}
\title{Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data}
\author{Valerie Hayot-Sasson}
\maketitle
\begin{abstract}
  Text of abstract.  
\end{abstract}
\tableofcontents
\chapter{Introduction}
intro here
\chapter{BigData in neuroscience}
    \note{Likely will not be split in two separate sections}
    \section{large images}
        \begin{itemize}  
            \item BigBrain
            \item Micro CT 
            \item EM 
        \end{itemize}
    \section{large datasets}
    	\note{off the top of my head, but need to double check}
        \begin{itemize}
            \item HCP
            \item ADNI
            \item OpenFMRI
        \end{itemize}
    An effective engine to process such data requires the following characteristics
        \begin{itemize}
            \item in-memory computing
            \item data locality
            \item lazy evaluation
        \end{itemize}
\chapter{Workflow engines for neuroimaging data}
    \begin{itemize}
        \item Nipype
        \item PSOAM
        \item SPM
        \item these engines do not currently support processing big data
      	\begin{itemize}
        		\item PSOAM - can't do data locality
		\item none do in-memory processing?
	\end{itemize}
    \end{itemize}
\chapter{CBRAIN}
\chapter{Domain nonspecific BigData frameworks}
	\section{mapreduce}
		\begin{itemize}
			\item many computations can be described through map and reduce
			\item fault tolerant
		\end{itemize}
	\section{spark}
		\begin{itemize}
			\item based on map-reduce
			\item in-memory processing
			\item lazy evaluation
			\item general framework
		\end{itemize}
	\section{Hadoop Distributed file system}
		\note{maybe should go in between mapreduce and spark}
		\begin{itemize}
			\item enables data-locality in Spark/ decouples data locality logic from mapreduce\
			\item data replication
			\item fault-tolerance
		\end{itemize}
\chapter{Current status of Big Data frameworks in neuroscience}
	\section{Ariel's paper}
	\section{Thunder}
\chapter{Use of containers in Workflow engines}
	\section{use of containers in nipype, psoam, spm}
	\section{using containers w/ Spark}

\chapter{Summaries}

This section contains summaries and/or notes on the 5 main papers to aid with writing and structuring of ideas.
\section{MapReduce}
Summary of ~\cite{mapred}

@@

\section{Apache Spark}
\cite{spark}
\section{Thunder}
\cite{thunder}
\section{NiPype}
\cite{nipype}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Body of Thesis goes here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
